Slitasje og kjørespor

### 2022-11-09 naturtype2.Rmd
add lost nin types

## Naturetypes, condition variables, and their linkage to NiN main types
Only a subset of nature types are mapped. How well do these mapped units/areas represent the range of nature types that is included for each main ecosystem group? And what condition variables do we have available for each of these?

@@

We will only include our target ecosystems, and we will exclude *Hule eiker*.
```{r}
target <- c("Semi-naturlig mark",
            "Våtmark",
            "Naturlig åpne områder under skoggrensa")
dat <- dat[dat$hovedøkosystem %in% target,]
dat <- dat[dat$naturtype != "Hule eiker",]
```

@@

Adding the non-mapped semi-natural types
```{r}
semi[semi %!in% ntyp_fill$NiN_mainType]
```
```{r}
ntyp_fill2 <- ntyp_fill %>%
  add_row(NiN_mainType = "T40", Ecosystem = "Semi-naturlig mark", NiN_mainTypeCoverage = "Not mapped", km2 = 0)
```

@@

@@

For *Semi-naturlig mark* we have quite good thematic coverage for the three main types. The other three types probably makes up a considerably smaller area, but note that T33 has some coverage, and is classes as *all (-2018)*. Of the three main ecosystems, semi-naturlig mark dominates clearly. I will need to look for NiN variables associated with the mapping units for these main NiN types. I can also possibly explore the distribution of the mapped polygons in environmental space and compare it against AR5 as a reference, but I'm not sure how good AR5 is for anything whihc is not cropland.

>>>>

## Resarch question
Only a subset of nature types are mapped. How well do these mapped units/areas represent the range of nature types that is included for each main ecosystem group? And what condition variables do we have available for each of these?

@@

We will only include our target ecosystems, and we will exclude *Hule eiker*.

```{r}
unique(dat$hovedøkosystem)
```

```{r}
target <- c("Semi-naturlig mark",
            "Våtmark",
            "Naturlig åpne områder under skoggrensa")
dat <- dat[dat$hovedøkosystem %in% target,]
dat <- dat[dat$naturtype != "Hule eiker",]
```

@@

Adding the non-mapped semi-natural types
```{r}
semi[semi %!in% ntyp_fill$NiN_mainType]
```
```{r}
ntyp_fill2 <- ntyp_fill2 %>%
  add_row(NiN_mainType = "T40", Ecosystem = "Semi-naturlig mark", NiN_mainTypeCoverage = "Not mapped", km2 = 0)
```

@@

### Export summary dataset
```{r, eval = F}
saveRDS(ntyp_fill2, "data/naturetypes/natureType_summary.rds")
```

@@

For *Semi-naturlig mark* we have quite good thematic coverage for the three main types. The other three types probably makes up a considerably smaller area, but note that T33 has some coverage, and is classes as *all (-2018)*. Of the three main ecosystems, semi-naturlig mark dominates clearly. I will need to look for NiN variables associated with the mapping units for these main NiN types. I can also possibly explore the distribution of the mapped polygons in environmental space and compare it against AR5 as a reference, but I'm not sure how good AR5 is for anything which is not cropland.
